Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-02-06 Manuscript/PLoSONESubmission/TEM_draft.tex
PLoS One Submission init

\newpage
\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{AllMethods-RF+Tr-colour.pdf}
\caption{ }
\end{figure}

\newpage
\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{ML+Baycon-AllParam-RF+Tr-BW.pdf}
\caption{ }
\end{figure}

\newpage
\begin{figure}
\centering
    \includegraphics[width=1\textwidth]{PairwiseComp-Baycon-RF+Tr-colour.png}
\caption{ }
\end{figure}

>>>>

\newpage
\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{AllMethods-RF_Tr-colour.pdf}
\caption{ }
\end{figure}

\newpage
\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{ML_Baycon-AllParam-RF_Tr-BW.pdf}
\caption{ }
\end{figure}

\newpage
\begin{figure}
\centering
    \includegraphics[width=1\textwidth]{PairwiseComp-Baycon-RF_Tr-colour.png}
\caption{ }
\end{figure}
